---
title: "main"
output: html_document
date: "2022-10-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("tidyr")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("readr")
# install.packages("lubridate")
# install.packages("Plotly")
# install.packages("hrbrthemes")
# install.packages("viridis")
# install.packages("ggridges")
# install.packages("highcharter")
# install.packages("rio")
# install.packages("purrr")

library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(plotly)
library(hrbrthemes)
library(viridis)
library(ggridges)
library(highcharter)
library(rio)
library(purrr)
library(stringr)
library(scales)
library(stringr)
```

```{r}
df <- read_csv("data_input/HRdataset_v14.csv")
```

```{r}
glimpse(df)
```

```{r}
class(df$CitizenDesc)
```
```{r}
unique(df$CitizenDesc)
```
## CLEANSING ## 

# To Factor
1. RecruitmentSource : 9 levels
2. PerformanceScore : 3 levels
3. EmpSatisfaction : 3 levels
4. Department : 5 levels
5. EmploymentStatus : 2 levels
6. TermReason : 18 levels
7. sex : 2 levels
8. CitizenDesc : 2 levels

# To Date
1. DOB
2. DateofHire
3. DateofTermination
4. LastPerformanceReview_Date

# To Logical
1. Married Id
2. FromDiversityJobFairID

#drop columns
1. ZIP
2. HispanicLatino
3. RaceDesc
```{r}
df_clean <- df %>% 
  mutate_at(.vars = c("RecruitmentSource", "PerformanceScore", "EmpSatisfaction", "Department", "EmploymentStatus", "TermReason", "Sex","CitizenDesc" ), 
            .funs = as.factor) %>% 
  mutate_at(.vars = c("MarriedID", "FromDiversityJobFairID"), 
            .funs = as.logical)

df_clean$DateofHire <- mdy(df$DateofHire) 
df_clean$DOB <- mdy(df$DOB) 
df_clean$DateofTermination <- mdy(df$DateofTermination)
df_clean$LastPerformanceReview_Date <- mdy(df$LastPerformanceReview_Date)

df_clean <- select(df_clean, -Zip, -HispanicLatino, -RaceDesc)
glimpse(df_clean)
```
## ANALYSING ##

```{r}
df_clean
```


```{r}
plot1 <- 
  ggplot(data= df_clean, mapping = aes(x = Department, y = EngagementSurvey)) +
  geom_boxplot(mapping = aes(fill = Department))

ggplotly(plot1)
```

```{r}
plot5 <- 
  ggplot(data = df_clean, mapping = aes(x = df_clean$EngagementSurvey, y = Salary))+
  geom_line()

ggplotly(plot5)
```

```{r}
hc <- hchart(
  density(df_clean$Salary), type = "area", 
  color = "steelblue", name = "Male"
  )

hc
```

```{r}
p2 <- ggplot(data=df_clean, aes(x=Salary, group=EmpSatisfaction, fill=EmpSatisfaction)) +
    geom_density(adjust=1.5, alpha=.4) +
    theme_ipsum()

ggplotly(p2)
```
```{r}
hchart(df_clean, 
         type = "column", 
         hcaes(x = PerformanceScore, 
               y = Salary, 
               group = Department))
```
```{r}
hchart(df_clean,
       type = "column", 
       hcaes(x = Department, 
             y = Salary,
             group = EmpSatisfaction))%>% 
    hc_tooltip(
      useHTML = TRUE
    ) %>% hc_exporting(enabled = TRUE) 
  # %>% 
  #   hc_tooltip(crosshairs = TRUE,
  #              shared = TRUE, borderWidth = 2)
```


```{r}
hc <- hchart(df_clean, "packedbubble", hcaes(name = Position,value = EngagementSurvey,group = RecruitmentSource))

q95 <- as.numeric(quantile(df_clean$EngagementSurvey, .95))

hc %>% 
  hc_tooltip(

        useHTML = TRUE,
    pointFormat = "<b>{point.name}:</b> {point.value}"
  ) %>% 
  hc_plotOptions(
    packedbubble = list(
      maxSize = "50%",
      zMin = 0,
      layoutAlgorithm = list(
        gravitationalConstant =  0.05,
        splitSeries =  TRUE, # TRUE to group points
        seriesInteraction = TRUE,
        dragBetweenSeries = TRUE,
        parentNodeLimit = TRUE
      ),
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}",
        filter = list(
          property = "y",
          operator = ">",
          value = q95
        ),
        style = list(
          color = "black",
          textOutline = "none",
          fontWeight = "normal"
        )
      )
    )
  )
```


```{r}
options(dplyr.summarise.inform = FALSE)

df_baru <- 
  select(df_clean, Department, Position, Salary) %>% 
  arrange(desc(Salary)) 
  
  df_baru_2 <- df_baru %>% 
  group_by(Department) %>% 
  summarise(dailyAvg = mean(Salary))

drilldown <- df_baru %>%
  # group_by(Department, Position, .add = T) %>% 
  group_nest(Department) %>%
  mutate(
    id = Department,
    type = "column",
    data = map(data, ~ .x %>%
      mutate(
        name = Position,
        y    = Salary
      ) %>%
      list_parse())
  )

mygraph <- hchart(
  df_baru_2,
  "column",
  hcaes(x = Department, y = dailyAvg, name = Department, drilldown = Department),
  name = "Salary",
  colorByPoint = TRUE
)

mygraph <- mygraph %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series = list_parse(drilldown)
  ) 

mygraph <- mygraph %>%
  hc_tooltip(
    useHTML = TRUE 
  ) %>% 
  hc_yAxis( title = "") %>% 
  hc_xAxis( title = "" ) %>%
  hc_title(text = "Salary" )

mygraph
```

```{r}
unique(df_clean$Department)
```
```{r}
hchart(df_clean, "scatter", hcaes(x= EngagementSurvey,y= SpecialProjectsCount, name = Position, group = Department)) %>% 
    hc_chart(type = "scatter") %>%
    hc_tooltip(
      headerFormat = "",
      pointFormat = "<b>{point.Position}</b> is in <b>{point.Department}</b>"
    ) 
```
```{r}
unique(df_clean$ManagerName)
```
```{r}
hchart(df_clean, "organization", hcaes(from = ManagerName, to = Employee_Name)) %>% 
  hc_chart(inverted = TRUE)
```

```{r}
hchart(df_clean, "lollipop", hcaes(name = Employee_Name, low = Absences ),name = "Absences") %>% 
  hc_xAxis(type = "category") %>% 
  hc_yAxis(labels = list(format = "{value}"))
```

```{r}
df_clean_2 <- df_clean %>% mutate_at(.vars = c("EmpSatisfaction"), .funs = as.numeric) 
hchart(df_clean_2, "lollipop", hcaes(name = Employee_Name, low = EmpSatisfaction),name = "EmpSatisfaction") %>% 
      hc_xAxis(type = "category") %>% 
      hc_yAxis(labels = list(format = "{value}")) %>% 
      hc_title(text="Employee Satisfaction under {var}",align="center")
```
```{r}
mean(df$Absences)
```

